% !TEX TS-program = xelatex
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{resume}
\usepackage{linespacing_fix}
\usepackage{cite}

\begin{document}
\pagenumbering{gobble}

\name{Haixiang Wang}
\contactInfo{(+86) 156-6207-7668}{jt846962421@gmail.com}{AI Agent Engineer}{GitHub: @JackWPP}

\section{Education}
\datedsubsection{\textbf{Beijing University of Chemical Technology} -- B.E. Computer Science}{Sep 2021 - Jun 2026}
\textbf{Awards:} First Prize in "Challenge Cup" Beijing Competition (2025), National Second Prize in Computer Skills Challenge (2024), Second Prize in iCAN Competition Beijing Region (2024).

\datedsubsection{\textbf{Beijing University of Chemical Technology} -- M.E. Chemical Engineering}{Sep 2026 - Jun 2029}
Recommended admission (graduate exam exemption). Research: Computer Vision-based Bubble Tracking for Water Electrolysis.

\section{Technical Skills}
\begin{itemize}[parsep=0.1ex, leftmargin=1.2pc]
  \item \textbf{Languages:} Python, C/C++, Java, Shell, SQL
  \item \textbf{AI/DL:} PyTorch, RAG, Prompt Engineering, Dify, Multi-Agent Systems
  \item \textbf{Frameworks:} FastAPI, React, Flask $|$ \textbf{Tools:} MySQL, MongoDB, Git, Linux
  \item \textbf{Expertise:} LLM Applications, Computer Vision, Private Deployment, Multimodal Processing
\end{itemize}

\section{Project Experience}
\datedsubsection{\textbf{PCBTool.AI} -- Intelligent PCB Design System, \textit{Algorithm Lead}}{2025 - Present}
\begin{itemize}[parsep=0.1ex, leftmargin=1.2pc]
  \item Built multimodal intelligent system using LLMs and RAG, supporting natural language and circuit diagram inputs; auto-generates documentation, deployment guides, and PCB layouts.
  \item Led Dify framework private deployment; improved LLM response accuracy by \textbf{40\%+} through multi-Agent collaboration and prompt engineering.
  \item \textbf{Result:} Won \textbf{First Prize} in "Challenge Cup" National Competition Beijing Region.
\end{itemize}

\datedsubsection{\textbf{ROBOT-XZC Technical Services}, \textit{Founder/Tech Lead}}{2023 - Present}
\begin{itemize}[parsep=0.1ex, leftmargin=1.2pc]
  \item Built campus technical service platform; completed \textbf{2000+} repairs and 3D printing services with 95\%+ satisfaction.
  \item Conducted \textbf{100+} robotics and 3D printing training sessions, covering \textbf{1000+} participants.
  \item Developed dual-driven model (repair profit + hardware R\&D); achieved monthly revenue of 8,000 RMB.
\end{itemize}

\section{Campus Involvement}
\datedsubsection{\textbf{BUCT North Campus Affairs Office}, \textit{Official Photographer}}{2023 - 2025}
\begin{itemize}[parsep=0.1ex, leftmargin=1.2pc]
  \item Led photography for major events and VIP visits; created promotional content for official media.
  \item Produced "First Photo" orientation videos achieving \textbf{100,000+} views on official platforms.
\end{itemize}

\section{Honors \& Awards}
\begin{itemize}[parsep=0.1ex, leftmargin=1.2pc]
  \item First Prize, "Challenge Cup" AI Competition (Beijing), 2025
  \item National Second Prize, Computer Skills Challenge, 2024
  \item Provincial Second Prize, Lanqiao Cup Software Competition, 2023
  \item National Excellence, Innovation Training Program (Body Area Network Health Monitor), 2023
  \item Second Prize, iCAN Innovation Competition (Beijing), 2024
\end{itemize}

\end{document}
